Creating an Evolution Simulator for Protein Low Complexity Regions and Attempting to Utilize it for an Approximate Bayesian Computation

### 2023-04-05 beap_pres_dec2022/beap_pres_dec.tex
Updated pres
BUS PRES UPDATES

% Title page details: 
\title[BEAP Dec 2022]{Creating an Evolution Simulator for Protein Low Complexity Regions and Attempting to Utilize it for an Approximate Bayesian Computation} 
\author{Alexander Turco}
\date{December 5, 2022}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

%Extra packages
\usepackage{makecell}

@@

	% Outline frame - SLIDE 2
	\begin{frame}{Overview}

@@

@@

	%SLIDE 8 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about LCRs and their Evolution?}

	\begin{frame}{What we Did in this Study}
		\begin{itemize}
			\item Utilized \texttt{C++} to build an evolution simulator which altered protein sequences via point mutations, insertions, and deletions \newline
			\item Tested the simulator with various insertion/deletion rates and mutation rates \newline
			\item Attempted to program an ABC-MCMC in \texttt{C++} using the evolution simulator as an important step in the algorithm, in order to estimate parameters like mutation and indel rates.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{LCR Simulator Results}
		\includegraphics[height=6cm, width=\textwidth]{im0.01-0.1-0.5.jpeg}
	\end{frame}

	\begin{frame}{LCR Simulator Results 2}
		\includegraphics[height=7cm, width=\textwidth]{im1-2-10.jpeg}
	\end{frame}

	\begin{frame}{LCR Simulator Results 3}
		\includegraphics[height=7cm, width=\textwidth]{m0.01-0.1-0.5.jpeg}
	\end{frame}

	\begin{frame}{LCR Simulator Results 4}
		\includegraphics[height=7cm, width=\textwidth]{m1-2-10.jpeg}
	\end{frame}

>>>>

% Title page details: 
\title[BEAP Dec 2022]{Creating an Evolution Simulator for Protein Low Complexity Regions and Attempting to Utilize it for an Approximate Bayesian Computation} 
\author{Alexander Turco}
\date{April 13, 2023}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

%Extra packages
\usepackage{makecell}
\usepackage{verbatim}
\usepackage{setspace}

@@

	% Outline frame - SLIDE 2
	\begin{comment}
		\begin{frame}{Overview}

@@

		\end{frame}
	\end{comment}

	%SLIDE 8 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about Low Complexity Regions and their Evolution?}

@@

	\begin{frame}{What we Did in this Study}
		\begin{itemize}
			\item Utilized \texttt{C++} to build an evolution simulator which altered protein sequences via point mutations, insertions, and deletions \newline
			\item Tested the simulator with various insertion/deletion rates and mutation rates \newline
			\item Attempted to program an approximate bayesian computation markov chain monte carlo algorithm (ABC-MCMC) in \texttt{C++} using the evolution simulator as an important step in the algorithm, in order to estimate parameters like mutation and indel rates.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Lower Indel Rates Produce Less LCRs}
		\begin{columns}	
			\column{0.5\textwidth}
			\centering
			\begin{figure}
					\includegraphics[height=6cm, width=6cm]{ind_figures/ii0.1} \\~\\
				\caption{\centering Indel Rate = 0.1 Mutation Rate = 1}
			\end{figure} \pause

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=6cm, width=6cm]{ind_figures/ii0.5} \\~\\
				\caption{\centering Indel Rate = 0.5 Mutation Rate = 1}
			\end{figure}

	\begin{frame}{Higher Indel Rates Produce More LCRs}
		\begin{columns}	
			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=3cm, width=6cm]{ind_figures/ii1} \\~\\
				\vspace{-0.5cm}\tiny\caption{\centering Indel Rate = 1 Mutation Rate = 1}
			\end{figure} \pause

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=3cm, width=6cm]{ind_figures/ii2} \\~\\
				\vspace{-0.5cm}\tiny\caption{\centering Indel Rate = 2 Mutation Rate = 1}
			\end{figure} \pause

		\begin{figure}
			\includegraphics[height=3cm, width=\textwidth]{ind_figures/ii10}
			\vspace{-1cm}\caption{\centering Indel Rate = 10 Mutation Rate = 1}
		\end{figure}

	\begin{frame}{Lower Mutation Rates Produce More LCRs}
		\begin{columns}	
			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=3cm, width=6cm]{ind_figures/im0.01} \\~\\
				\vspace{-0.5cm}\tiny\caption{\centering Indel Rate = 1 Mutation Rate = 0.01}
			\end{figure} \pause

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=3cm, width=6cm]{ind_figures/im0.1} \\~\\
				\vspace{-0.5cm}\tiny\caption{\centering Indel Rate = 1 Mutation Rate = 0.1}
			\end{figure} \pause

		\begin{figure}
			\includegraphics[height=3cm, width=\textwidth]{ind_figures/im0.5}
			\vspace{-0.7cm}\caption{\centering Indel Rate = 1 Mutation Rate = 0.5}
		\end{figure}
	\end{frame}

	\begin{frame}{Large Mutation Rates Prevent the Formation of LCRs}
		\begin{columns}	
			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=3cm, width=6cm]{ind_figures/im1} \\~\\
				\vspace{-0.5cm}\tiny\caption{\centering Indel Rate = 1 Mutation Rate = 1}
			\end{figure} \pause

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[height=3cm, width=6cm]{ind_figures/im2} \\~\\
				\vspace{-0.5cm}\tiny\caption{\centering Indel Rate = 1 Mutation Rate = 2}
			\end{figure} \pause

		\begin{figure}
			\vspace{-0.4cm}\includegraphics[height=3cm, width=\textwidth]{ind_figures/im10}
			\vspace{-0.7cm}\caption{\centering Indel Rate = 1 Mutation Rate = 10}
		\end{figure}
	\end{frame}
